Two subtle problems with over-representation analysis

### 2024-07-18 manuscript/manuscript.Rmd
ms work

## Does FCS have better sensitivity than ORA with real RNA-seq data?

@@

![**Figure 4. Downsampling confirms higher sensitivity for FCS over ORA.
(A) The number of significant pathways identified in downsampled data that are consistent
with findings in the full dataset, using FCS (fgsea) and ORA (fora) methods.
(B) The number of significant pathways identified in downsampled data that are not
consistent the full dataset.
(C) The proportion of pathways in downsampled data that are inconsistent with the full
dataset.
All values are the median of 50 simulations.](../analysis/fig4.png "Figure 4A shows that fgsea is more sensitive than fora. Figure 4B shows fgsea has higher absule number of false positives, but Figure 4C shows that as a proportion of all findings fgsea has lower false positive rate than fora.")

>>>>

### Exploring sensitivity in real RNA-seq data

@@

![**Figure 4. Downsampling confirms higher sensitivity for FCS over ORA.**
(A) The number of significant pathways identified in downsampled data that are consistent
with findings in the full dataset, using FCS (fgsea) and ORA (fora) methods.
(B) The number of significant pathways identified in downsampled data that are not
consistent the full dataset.
(C) The proportion of pathways in downsampled data that are inconsistent with the full
dataset.
All values are the median of 50 simulations.](../analysis/fig4.png "Figure 4A shows that fgsea is more sensitive than fora. Figure 4B shows fgsea has higher absule number of false positives, but Figure 4C shows that as a proportion of all findings fgsea has lower false positive rate than fora.")
